Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-14 documents/BrazilSlides/slides.tex
Updates from ShareLaTeX

\documentclass[
    % hyperref={bookmarks=false,colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
    xcolor={dvipsnames},
]{beamer}

% \usepackage{pgfpages} % For viewing slides on the right
\usepackage[warningthreshold=0.95]{resizegather} % For resizing gather environment to fit massive equations
\setbeameroption{show notes} % Shows notes on the right of the main slides
% \setbeameroption{show notes on second screen}
\usefonttheme[onlymath]{serif} % For serif font in math mode
\usepackage[round]{natbib} % Needed for Author name citations
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}
\input{../../figures/causal_structures/formatting} % Causal structure formatting for tikz
\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}
\renewcommand{\tcdot}{\cdot} % Tentative cdot, not sure if I want to keep dots

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.C.~Fraser\inst{1}}
\institute[PI]
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada
}
\date[QN 2016]{Quantum Networks, 2016}

@@

\begin{frame}[allowframebreaks]
    \frametitle{References}
    \todo[TC]{Figure out how to get references at the end}
    \setbeamertemplate{bibliography item}{\insertbiblabel}
    \bibliographystyle{plainnat}
    \bibliography{../references}{}
\end{frame}

@@

\begin{frame}
    \frametitle{Introduction}
    \note[item]{Thank International Institute for Physics (IIP) for support}
    \note[item]{Thank Perimeter Institute for Theoretical Physics (PI) for support}
\end{frame}
\begin{frame}
    \frametitle{Objective}
    \begin{itemize}
        \item Derive causal compatibility/locality inequalities that distinguish quantum distributions from classical ones
        \item Specifically for the Triangle Scenario (TS)
    \end{itemize}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
    \end{center}
    \note[item]{Research project's goal was to derive new causal compatibility inequalities that distinguish quantum correlations from classical correlations}
    \note[item]{More specifically, the ambition of the project is to obtain such inequalities that constraint compatibility with The Triangle Scenario}
    \note[item]{Triangle Scenario has be studied extensively before}
\end{frame}

\begin{frame}
    \frametitle{Objective Cont'd}
    \begin{itemize}
        \item In~\citet{Branciard_2012} it was noted that characterizing locality in TS remained an open problem and that identifying compatibility constraints in this configuration \textbf{seemed challenging}
        \item In~\citet{Fritz_2012}, Fritz demonstrated that TS is the \textbf{smallest} correlation scenario in which their exists quantum incompatible distributions (proof without inequalities)
        \item In~\citet{Henson_2014}, TS was classified as an \textbf{interesting} causal structure: conditional independence relations are not a sufficient characterization of compatibility
        \item Several other authors (see~\cite{Steudel_2010},~\cite{Chaves_2014},~\cite{Inflation}, $\ldots$) have investigated TS without achieving research objective
    \end{itemize}
    \note[item]{At the time of publishing~\citet{Branciard_2012}, problem seems hard.}
    \note[item]{Important because its smallest correlation scenario with quantum non-locality.}
    \note[item]{Compatibility can not be determined from conditional independence relations (there are none)}
    \note[item]{It would be interesting to find quantum non-locality in the triangle scenario that does not rely on Bell's theorem.}
\end{frame}

\begin{frame}
    \frametitle{This Talk}
    \begin{itemize}
        \item Report the discovery of such inequalities
        \item Explain how these inequalities were obtained
        \item Discuss quantum distributions that violate compatibility inequalities
        \item Attempts at finding new quantum distributions different than those proposed by~\cite{Fritz_2012}
        \item Briefly discuss symmetric inequalities
    \end{itemize}
    \note[item]{The purpose of this talk is to present these new-found inequalities and explain how they were obtained}
    \note[item]{Additionally I will talk about my attempts at using these inequalities to find new incompatible quantum distributions}
    \note[item]{In doing so, will discuss how we obtained symmetric compatibility inequalities that have violations in the Triangle Scenario}
\end{frame}

\begin{frame}
    \frametitle{Example Inequality}
    \begin{itemize}
        \item Quick example/preview:
    \end{itemize}
    \input{../../figures/inequalities/nosymwitness_ineq_print_pretty}
    \begin{itemize}
        \item $\prob[][abc]$ shorthand for $\prob[ABC][abc]$
        \item Four outcomes for each $A, B, C$
        \item Polynomial in $\prob[ABC]$, marginals $\prob[AB]$, $\prob[BC]$, $\prob[AC]$, $\prob[A]$, $\prob[B]$, $\prob[C]$
    \end{itemize}
    \note[item]{As a quick example or preview of what is to come, here is a an example inequality admits quantum violations in the triangle scenario}
    \note[item]{Some features of note: inequality is polynomial in $\prob[ABC]$ and its marginals}
\end{frame}

% \begin{frame}
%     \frametitle{Notation}
%     \begin{itemize}
%         \item A subset of $V \subset \jointvar$ is a \term{marginal context}
%         \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
%         \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
%     \end{itemize}
% \end{frame}

\begin{frame}
    \frametitle{Notation}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \begin{itemize}
        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
        \item \term{Marginal scenario} $\mscenario = \bc{V_1, \ldots, V_k}$
        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        % \item Marginal scenario forms a \textit{simplicial complex}
        % \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        \item \term{Joint random variables} $\jointvar = {\bigcup}_{i} V_i = \bc{v_1, \ldots, v_n}$
        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
    \end{itemize}
    \note[item]{Before continuing, I will define exactly what I mean by causal compatibility}
    \note[item]{Causal compatibility refers to the compatibility between causal structures and marginal models}
    \note[item]{Marginal model is collection of probability distributions over sets of random variables}
    \note[item]{Marginal scenario refers to the those sets of random variables}
    \note[item]{The complete set of random variables are the joint random variables}
\end{frame}

@@

\begin{frame}
    \frametitle{Causal Compatibility}
    \textbf{Question:} Which marginal models $\prob^{\mscenario}$ are \term{compatible} with a causal structure $\graph$?\\
    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
    \begin{enumerate}
        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
    \end{enumerate}
    \textbf{Inequality:} A \term{casual compatibility inequality} $I$ is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
\end{frame}

\begin{frame}
    \frametitle{Deriving Inequalities}
    Two necessary components to compatibility:
    \begin{enumerate}
        \item[1.] \term{Marginal problem}: $\forall V \in \mscenario : \prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
        \begin{itemize}
            \item Is the marginal model contextual or non-contextual?
            \item 3 distinct ways to tackle this problem
            \begin{enumerate}
                \item[1.] Convex hull, Polytope projection, Fourier-Motzkin
                \item[2.] Possibilistic Hardy Inequalities (Hypergraph transversals)
                \item[3.] Linear Program Feasibility/Infeasibility
            \end{enumerate}
        \end{itemize}
    \end{enumerate}
    \begin{enumerate}
        \item[2.] \term{Markov Separation}: $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \begin{itemize}
            \item Much harder to determine since latent nodes $\nodes_O$ have unspecified behaviour
            \item It is possible to turn Markov Separation problem into a Marginal problem (at least partially)
        \end{itemize}
    \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Inflation Technique}
    Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
        And '$\sim$' is a \term{copy-index} equivalence relation
        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
    \end{definition}
\end{frame}

@@

\begin{frame}
    \frametitle{$d$-Separation Polynomial}

@@

\begin{frame}
    \frametitle{Distribution Vectors}
    \begin{itemize}
        \item \term{Joint Distribution Vector $\probvec^{\jointvar}$}
        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
        \item \term{Marginal Distribution Vector $\probvec^{\mscenario}$}
        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item Marginal Problem as linear program
        \begin{align*}
            \probvec^{\mscenario}_m &= {\sum}_{j} M_{m,j} \probvec^{\jointvar}_j \\
            \probvec^{\mscenario} &= M \tcdot \probvec^{\jointvar}
        \end{align*}
        \item \term{Incidence matrix} $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m = j|_{\Dom{m}} \\
            0 & \text{otherwise}
        \end{cases} \]
        \begin{gather*}
        \# \text{Columns} = \abs{\Events{\jointvar}} = \prod_{v \in \jointvar} \abs{O_{v}} \\
        \# \text{Rows} = \abs{\Events{\mscenario}} = \sum_{V \in \mscenario} \prod_{v \in V} \abs{O_{v}}
        \end{gather*}

    \end{itemize}
\end{frame}

\begin{frame}[shrink=10]
    \frametitle{Example}
    Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{A,B,C}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{A,B}, \bc{B,C}, \bc{A,C}}$. The incidence matrix becomes:
    \[ M = \kbordermatrix{
        (A,B,C) \:\: = & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
        (A=0, B=0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A=0, B=1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A=1, B=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
        (A=1, B=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
        (B=0, C=0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
        (B=0, C=1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
        (B=1, C=0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
        (B=1, C=1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
        (A=0, C=0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
        (A=0, C=1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
        (A=1, C=0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
        (A=1, C=1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
    } \]
\end{frame}

\begin{frame}
    \frametitle{Application to Large Inflation}
    \begin{columns}
        \column{0.6\linewidth}
            \begin{itemize}
                \item Find compatibility inequalities for TS by finding non-contextuality inequalities for Large Inflation
                \item Marginal Scenario is the set of maximal pre-injectable sets
                \item 12 maximal pre-injectable sets (to follow)
            \end{itemize}
        \column{0.4\linewidth}
            \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
        \[ \# \text{Columns} = 4^{12} = 16,777,216 \]
        \[ \# \text{Rows} =  4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
    \end{itemize}
\end{frame}

@@

\section{Symmetries}
\begin{frame}
    \frametitle{Causal Symmetry}
    \begin{itemize}
        \item Desirable to find compatibility inequality $I$ such that
        \[ \forall \varphi \in \Perm{A,B,C} : \varphi\bs{I} = I \]
        \item Compatibility is independent of variable labels
        \[ \forall \varphi \in \Perm{\nodes} : I \stackrel{\text{com}}{\rightarrow} \graph \implies \varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \varphi\bs{\graph}  \]
        \item If $\varphi\bs{\graph} = \graph$ then $\varphi\bs{I} \stackrel{\text{com}}{\rightarrow} \graph$
    \end{itemize}
    \begin{definition}
        The \term{causal symmetry group} of causal structure $\graph$:
        \[ \Aut{\graph} = \bc{\varphi \in \Perm{\nodes} \mid \varphi\bs{\graph} = \graph} \]
        Strictly speaking, one needs to preserve observable nodes:
        \[ \Aut[\nodes_O]{\graph} = \bc{\varphi \in \Aut{\graph} \mid \varphi\bs{\nodes_O} = \nodes_O} \]
    \end{definition}
    \note<1>[item]{Fritz distribution is incompatible with Triangle scenario because party $C$ plays the role of measurement settings for both $A$ and $B$}
    \note<1>[item]{In order to find quantum distributions different from $P_F$ in the Triangle Scenario, it is therefore desirable to find a proof of its incompatibility (i.e. inequality) that is symmetric under exchange of parties}
    \note<1>[item]{Surprisingly, it is possible to do so!}
    \note<1>[item]{Here is how.}
    \note<1>[item]{First, we will formally define the symmetry group in question}
    \note<1>[item]{Causal symmetry group is the }
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
        \item Relative Phase Terms: $RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$
        \item Rotation Terms: $R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = 1 \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        \item Computationally efficient
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{n,m} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{m,n} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}

>>>>

\documentclass[
    hyperref={colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=MidnightBlue},
    xcolor={dvipsnames},
]{beamer}

\setbeameroption{show notes}
\usefonttheme[onlymath]{serif}

\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}

% === Causal structure formatting for tikz ===
\input{../../figures/causal_structures/formatting}

\renewcommand{\term}[1]{\textcolor{Mahogany}{#1}}

\title[Triangle Inequalities]{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario}
\author[Fraser]{T.~C.~Fraser\inst{1}}
\institute[PI]
{
    \inst{1}%
    Perimeter Institute for Theoretical Physics\\
    Ontario, Canada
}
\date[QN 2016]{Quantum Networks, 2016}

@@

\begin{frame}[allowframebreaks]
    \frametitle{References}
    \todo[TC]{Figure out how to get references at the end}
    \setbeamertemplate{bibliography item}{\insertbiblabel}
    \bibliographystyle{abbrv}
    \bibliography{../references}{}
\end{frame}

@@

\begin{frame}
    \frametitle{Introduction}
    \note[item]{\todo[TC]{}}
\end{frame}

\begin{frame}
    \frametitle{Notation}
    \begin{itemize}
        \item Complete set of random variables are the \term{joint random variables}
        \[ \jointvar = \bc{v_1, \cdots, v_n} \]
        \item A subset of $V \subset \jointvar$ is a \term{marginal context}
        \item \term{Marginal scenario} $\mscenario$
        \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \jointvar} \quad \jointvar = {\bigcup}_{i} V_i  \]
        \item Marginal scenario forms a \textit{simplicial complex}
        \[ V \in \mscenario, V' \subseteq V  \implies V' \in \mscenario \]
        \item Restrict focus to \textit{maximal} marginal scenario where only the largest contexts are present
        \[ \forall V_i, V_j \in \mscenario : V_i \not \subset V_j \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Notation Cont'd}
    \begin{itemize}
        \item \term{Marginal model} $\prob^{\mscenario}$ is collection of probability distributions
        \[ \prob^{\mscenario} = \bc{\prob[V_1], \ldots, \prob[V_k]} \]
        \item \term{Causal Structure} $\graph = \br{\nodes, \edges}$ is a directed acyclic graph (DAG)
        \item Nodes classified into \term{latent nodes} $\nodes_{L}$ and \term{observed nodes} $\nodes_{O}$
    \end{itemize}
    \todo[TC]{Insert generic causal structure}
\end{frame}

@@

\begin{frame}
    \frametitle{Causal Compatibility}
    \textbf{Question:} Is a marginal model $\prob^{\mscenario}$ \term{compatible} with a causal structure $\graph$?\\
    \[ \mscenario = \bc{V_1, \ldots, V_k \mid V_i \subset \nodes_O} \]
    \textbf{Answer:} $\prob^{\mscenario}$ is compatible with $\graph$ if there exists a set of \term{casual parameters}
    \[ \bc{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes} \]
    Such that for each $V \in \mscenario$, $\prob[V]$ can be recovered:
    \begin{enumerate}
        \item $\prob[\nodes] = \prod_{n\in\nodes}\prob[n \mid \Pa[\graph]{n}]$
        \item $\prob[V] = \sum_{\nodes \setminus V} \prob[\nodes]$
    \end{enumerate}

    A \term{casual compatibility inequality} is an inequality over $\prob^{\mscenario}$ that is satisfied by all compatible $\prob^{\mscenario}$
    \note<1>[item]{}
\end{frame}

\begin{frame}
    \frametitle{Inflation Technique}
    \begin{itemize}
        \item Developed by Wolfe, Spekkens, and Fritz \cite{Inflation}
    \end{itemize}
    \begin{definition}
        An \term{inflation} of a causal structure $\graph$ is another causal structure $\graph'$ such that:
        \[ \forall n' \in \nodes', n' \sim n \in \nodes: \AnSub[\graph']{n'} \sim \AnSub[\graph]{n} \]
        Where $\AnSub[\graph]{n}$ denotes the ancestral sub-graph of $n$ in $\graph$
        \[ \AnSub[\graph]{n} = \Sub[\graph]{\An[\graph]{n}} \]
        And '$\sim$' is a \term{copy-index} equivalence relation
        \[ A_1 \sim A_2 \sim A \not \sim B_1 \sim B_2 \sim B \]
    \end{definition}

@@

@@

\begin{frame}
    \frametitle{Incidence Matrix}
    \begin{itemize}
        \item Incidence matrix $M$ is a bit-wise matrix
        \item Row-indexed by marginal events $m \in \Events{\mscenario}$
        \item Column-indexed by joint events $j \in \Events{\jointvar}$
        \[ M_{m,j} = \begin{cases}
            1 & m \text{ compatible with } j \\
            0 & \text{otherwise}
        \end{cases} \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Application to Large Inflation}
    \begin{columns}
        \column{0.6\linewidth}
            \begin{itemize}
                \item Tackling Large inflation
                \item 12 pre-injectable sets (to follow)
            \end{itemize}
        \column{0.4\linewidth}
            \scalebox{0.5}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{Large Inflation Incidence}
    \begin{itemize}
        \item Joint variables are all of the observable nodes $\nodes_O' = \jointvar$
        \[ \jointvar = \bc{A_1, A_2, A_3, A_4,B_1, B_2, B_3, B_4,C_1, C_2, C_3, C_4} \]
        \item Marginal scenario is composed of pre-injectable sets $\mscenario = \PreInj[\graph]{\graph'}$
        \item Inequalities Violated by Fritz distribution are inherently $4$-outcome
        \item Incidence matrix $M$ is very large $\sim 2.25 \textsf{Gb}$
        \[ \# \text{Columns} = \prod_{v \in \jointvar} O_{v} = 4^{12} = 16,777,216 \]
        \[ \# \text{Rows} = \sum_{V \in \mscenario} \prod_{v \in V} O_{v} = 4\times 4^{6} + 8 \times 4^{3} = 16,896 \]
    \end{itemize}
\end{frame}

@@

\section{Symmetries}
\begin{frame}
    \frametitle{Causal Symmetry}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} demonstrate a parameterization of $\s{U}\br{d}$ where the parameters are organized in a $d \times d$-matrix of real values $\la_{n,m}$
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} R_{m,n} RP_{n,m}}} \tcdot \bs{\prod_{l=1}^{d} GP_{l}} \]
        \item Global Phase Terms: $GP_{l} = \exp\br{iP_l \lambda_{l,l}}$
        \item Relative Phase Terms: $RP_{m,n} = \exp\br{i P_n \lambda_{n,m}}$
        \item Rotation Terms: $R_{n,m} = \exp\br{i \si_{m,n} \lambda_{m,n}}$
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Parameterizing Unitary Group Cont'd}
    \begin{itemize}
        \item Each parameter $\la_{n,m}$ has physical interpretation
        \item Degeneracies are easily eliminated such as global phase
        \[ \forall l = 1, \ldots, d : \la_{l,l} = 0 \implies GP_{l} = 1 \]
        \item Parameterize $U \in \s{U}\br{d}$ up to global phase denoted $\ti{U} \in \s{U}\br{d}$
        \item Computationally efficient
        \begin{alignat*}{2}
            GP_l &= \ident &&+ P_l \br{e^{i\la_{l,l}} - 1} \\
            RP_{m,n} &= \ident &&+ P_n \br{e^{i\la_{n,m}} - 1} \\
            R_{n,m} &= \ident &&+ \br{\ket{m}\bra{m} + \ket{n}\bra{n}} \br{\cos\lambda_{n,m} - 1} \\
            & &&+ \br{\ket{m}\bra{n} - \ket{n}\bra{m}} \sin\lambda_{n,m} \\
        \end{alignat*}
    \end{itemize}
\end{frame}
